\chapter*{Acknowledgments}
First of all, I am indebted to the GOD ALMIGHTY for giving me an opportunity to excel in my efforts to complete this seminar on time.

I am extremely grateful to Dr. V.O Rejini, Principal, Government College of Engineering Kannur and Dr. Rafeeque P.C, Head of Department, Department of Computer Science and Engineering, for providing all the required resources for the successful completion of my seminar.

My heartfelt gratitude to my seminar guide Dr. Rafeeque P.C, Head of Department, Computer Science and Engineering, for his valuable suggestions and guidance in the preparation of the seminar report. His experience guiding have really helped to get regular and positive feedback, suggestions and clarifications on various aspects during the seminar preparation.

I express my thanks to Prof. Bincy Antony M, Seminar Co-ordinator, and all staff members for all the help and co-ordination extended in bringing out this seminar successfully in time. She provided with various support materials and guidelines that have helped in developing a quality report.

I will be failing in duty if I do not acknowledge with grateful thanks to the authors of the references and other literatures referred to in this seminar. Last but not the least; I am very much thankful to my parents and friends who guided and supported me in every step which I took.

Finally, my thanks goes to all the people who have supported me to complete the seminar work directly or indirectly.

\hfill \studentName